---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# marc21r

<!-- badges: start -->

<!-- badges: end -->

{marc21r} is an R package for examining and analyzing [MARC21](https://www.loc.gov/marc/) files, a set of standards used to describe library materials such as books and journals. Currently, {marc21r} reads only MARC21 XML.

## Installation

You can install the development version of marc21r from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dojobo/marc21r")
```

## Example

The basic use case is to load a MARC XML file as a tibble. Each tag (001, 245, etc.) becomes a column whose name starts with `t`, e.g., `t001`, `t245`. Once so loaded, the dataset can be manipulated and analyzed using standard tidyverse tools.

```{r example}
library(marc21r)
library(dplyr)
collection <- read_marcxml("collection.xml")
collection %>% 
  select(t245, t260, t500)
```

For better readability, `tag_names()` can be applied to a MARC dataframe:

```{r}
collection %>% 
  select(t245, t260, t500) %>% 
  tag_names(style = "short")
```

